WI FastPlants: Heritability of number of cotelydons

### 2020-07-21 cotyledon-data-analysis.Rmd
minor change to plot

```{r, echo=FALSE}
p3 = ggplot(dat, aes(y = Generation, x = Cotyledons, fill = Generation)) +
  geom_jitter(pch = 21, alpha=0.3, width=0.2)+
  theme(
        plot.title = element_text(hjust=0.5, size=rel(1.8)),
        axis.title.x = element_text(size=rel(1.8)),
        axis.title.y = element_text(size=rel(1.8), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain"),
        axis.text.y = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain"),
        panel.background = element_blank(),
        axis.line = element_line(colour = "grey")##,
        )
p3
```

>>>>

```{r, echo=FALSE}
p3 = ggplot(dat, aes(x = Generation, y = Cotyledons, fill = Generation)) +
  geom_jitter(pch = 21, alpha=0.3, height=0.2)+
  theme(
        plot.title = element_text(hjust=0.5, size=rel(1.8)),
        axis.title.x = element_text(size=rel(1.8)),
        axis.title.y = element_text(size=rel(1.8), angle=90, vjust=0.5, hjust=0.5),
        axis.text.x = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain"),
        axis.text.y = element_text(colour="grey", size=rel(1.5), angle=0, hjust=.5, vjust=.5, face="plain"),
        panel.background = element_blank(),
        axis.line = element_line(colour = "grey")##,
        )
p3
```
